---
title: "PNN_song_knit"
author: "Fabiana"
date: "14 March 2017"
output: html_document
---

Set up environment to read files:
Need to 

* set working directory

* provide correct filename

* check data has been read as a data.frame



```{r setupenv, echo = FALSE, eval = TRUE}
setwd("/Volumes/myhome/GitHub/PNN/PNN_song_analysis")
pnnsong = read.csv("song_analysis.csv") 

class(pnnsong) #check it is a dataframe

library(ggplot2) #calls ggplot2 which should be installed
library(plyr) #need it for counts


# this grabs 2 cols and merges into 1 using a "_" as a separator between the 2 values to identify the 4 conditions
#using invivoenz_ichenz

pnnsong$method = paste(pnnsong$RAlesion, pnnsong$PNN_remov, sep="_") 

```
#Keys to what each group means:

RA Lesion: 0=sham; 1=yes
PNN_lesion: #sham1; #sham2, #sham3, 1,2,3
song_when:prelesion, preinjection, day 90;


* 0_0 -> no in vivo injection, no enzyme on immuno

* 0_1 -> no in vivo injection, enzyme on immuno

* 1_0 -> in vivo injection, no enzyme on immuno

* 1_1 -> in vivo injection, enzyme on immuno

Week 0: No injection, control

Week 1,2,3: Perfused 1,2,3 week after enzyme injection

#Box Plots



```{r boxplots, echo = FALSE, eval = TRUE}

groups<-levels(factor(pnnsong$method))  

pnnRA0 <- pnnsong[pnnsong$RAlesion==0,]
pnnRA1 <- pnnsong[pnnsong$RAlesion==1,]
pnn_0_sham1 <-pnnsong[pnnsong$method =="0_#sham1",]
pnn_0_sham2<-pnnsong[pnnsong$method =="0_#sham2",]
pnn_0_sham3<-pnnsong[pnnsong$method =="0_#sham3",]
pnn_0_0<-pnnsong[pnnsong$method =="0_0",]
pnn_0_1<-pnnsong[pnnsong$method =="0_1",]
pnn_0_2<-pnnsong[pnnsong$method =="0_2",]
pnn_0_3<-pnnsong[pnnsong$method =="0_3",]
pnn_1_sham1<-pnnsong[pnnsong$method =="0_#sham1",]
pnn_1_sham2<-pnnsong[pnnsong$method =="0_#sham2",]
pnn_1_sham3<-pnnsong[pnnsong$method =="0_#sham3",]
pnn_1_0<-pnnsong[pnnsong$method =="1_0",]
pnn_1_1<-pnnsong[pnnsong$method =="1_1",]
pnn_1_2<-pnnsong[pnnsong$method =="1_2",]
pnn_1_3<-pnnsong[pnnsong$method =="1_3",]

#ggplot(pnn, aes(song_when, intro_notes, colour=song_when))+
  #geom_point(size=1)
```

#Intro notes

```{r boxplots, echo = FALSE, eval = TRUE}
ggplot(pnn_0_sham1, aes(song_when, intro_notes, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,10))+
  geom_boxplot()

ggplot(pnn_0_sham2, aes(song_when, intro_notes, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,10))+
  geom_boxplot()

ggplot(pnn_0_sham3, aes(song_when, intro_notes, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,10))+
  geom_boxplot()

ggplot(pnn_0_0, aes(song_when, intro_notes, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,10))+
  geom_boxplot()

ggplot(pnn_0_1, aes(song_when, intro_notes, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,10))+
  geom_boxplot()

ggplot(pnn_0_2, aes(song_when, intro_notes, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,10))+
  geom_boxplot()

ggplot(pnn_0_3, aes(song_when, intro_notes, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,10))+
  geom_boxplot()

ggplot(pnn_1_sham1, aes(song_when, intro_notes, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,10))+
  geom_boxplot()

ggplot(pnn_1_sham2, aes(song_when, intro_notes, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,10))+
  geom_boxplot()

ggplot(pnn_1_sham3, aes(song_when, intro_notes, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,10))+
  geom_boxplot()

ggplot(pnn_1_0, aes(song_when, intro_notes, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,10))+
  geom_boxplot()

ggplot(pnn_1_1, aes(song_when, intro_notes, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,10))+
  geom_boxplot()

ggplot(pnn_1_1, aes(song_when, intro_notes, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,10))+
  geom_boxplot()

ggplot(pnn_1_3, aes(song_when, intro_notes, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,10))+
  geom_boxplot()

```


#Harmonic stacks

```{r boxplots, echo = FALSE, eval = TRUE}
ggplot(pnn_0_sham1, aes(song_when, harm_stacks, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,20))+
  geom_boxplot()

ggplot(pnn_0_sham2, aes(song_when, harm_stacks, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,20))+
  geom_boxplot()

ggplot(pnn_0_sham3, aes(song_when, harm_stacks, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,20))+
  geom_boxplot()

ggplot(pnn_0_0, aes(song_when, harm_stacks, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,20))+
  geom_boxplot()

ggplot(pnn_0_1, aes(song_when, harm_stacks, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,20))+
  geom_boxplot()

ggplot(pnn_0_2, aes(song_when, harm_stacks, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,20))+
  geom_boxplot()

ggplot(pnn_0_3, aes(song_when, harm_stacks, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,20))+
  geom_boxplot()

ggplot(pnn_1_sham1, aes(song_when, harm_stacks, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,20))+
  geom_boxplot()

ggplot(pnn_1_sham2, aes(song_when, harm_stacks, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,20))+
  geom_boxplot()

ggplot(pnn_1_sham3, aes(song_when, harm_stacks, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,20))+
  geom_boxplot()

ggplot(pnn_1_0, aes(song_when, harm_stacks, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,20))+
  geom_boxplot()

ggplot(pnn_1_1, aes(song_when, harm_stacks, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,20))+
  geom_boxplot()

ggplot(pnn_1_2, aes(song_when, harm_stacks, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,20))+
  geom_boxplot()

ggplot(pnn_1_3, aes(song_when, harm_stacks, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,20))+
  geom_boxplot()

```

#FM Sweeps

```{r boxplots, echo = FALSE, eval = TRUE}
ggplot(pnn_0_sham1, aes(song_when, FM_sweeps, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,50))+
  geom_boxplot()

ggplot(pnn_0_sham2, aes(song_when, FM_sweeps, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,50))+
  geom_boxplot()

ggplot(pnn_0_sham3, aes(song_when, FM_sweeps, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,50))+
  geom_boxplot()

ggplot(pnn_0_0, aes(song_when, FM_sweeps, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,50))+
  geom_boxplot()

ggplot(pnn_0_1, aes(song_when, FM_sweeps, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
 scale_y_continuous(limits=c(0,50))+
  geom_boxplot()

ggplot(pnn_0_2, aes(song_when, FM_sweeps, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,50))+
  geom_boxplot()

ggplot(pnn_0_3, aes(song_when, FM_sweeps, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,50))+
  geom_boxplot()

ggplot(pnn_1_sham1, aes(song_when, FM_sweeps, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,50))+
  geom_boxplot()

ggplot(pnn_1_sham2, aes(song_when, FM_sweeps, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,50))+
  geom_boxplot()

ggplot(pnn_1_sham3, aes(song_when, FM_sweeps, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,50))+
  geom_boxplot()

ggplot(pnn_1_0, aes(song_when, FM_sweeps, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,50))+
  geom_boxplot()

ggplot(pnn_1_1, aes(song_when, FM_sweeps, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,50))+
  geom_boxplot()

ggplot(pnn_1_2, aes(song_when, intro_notes, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,50))+
  geom_boxplot()

ggplot(pnn_1_3, aes(song_when, FM_sweeps, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,50))+
  geom_boxplot()

```

#Other

```{r boxplots, echo = FALSE, eval = TRUE}
ggplot(pnn_0_sham1, aes(song_when, other, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,50))+
  geom_boxplot()

ggplot(pnn_0_sham2, aes(song_when, other, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,50))+
  geom_boxplot()

ggplot(pnn_0_sham3, aes(song_when, other, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,50))+
  geom_boxplot()

ggplot(pnn_0_0, aes(song_when, other, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,50))+
  geom_boxplot()

ggplot(pnn_0_1, aes(song_when, other, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,50))+
  geom_boxplot()

ggplot(pnn_0_2, aes(song_when, other, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,50))+
  geom_boxplot()

ggplot(pnn_0_3, aes(song_when, other, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,50))+
  geom_boxplot()

ggplot(pnn_1_sham1, aes(song_when, other, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,50))+
  geom_boxplot()

ggplot(pnn_1_sham2, aes(song_when, other, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,50))+
  geom_boxplot()

ggplot(pnn_1_sham3, aes(song_when, other, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,50))+
  geom_boxplot()

ggplot(pnn_1_0, aes(song_when, other, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,50))+
  geom_boxplot()

ggplot(pnn_1_1, aes(song_when, other, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,50))+
  geom_boxplot()

ggplot(pnn_1_2, aes(song_when, other, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,50))+
  geom_boxplot()

ggplot(pnn_1_3, aes(song_when, other, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,50))+
  geom_boxplot()

```

#Total

```{r boxplots, echo = FALSE, eval = TRUE}
ggplot(pnn_0_sham1, aes(song_when, total, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,60))+
  geom_boxplot()

ggplot(pnn_0_sham2, aes(song_when, total, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,60))+
  geom_boxplot()

ggplot(pnn_0_sham3,aes(song_when, total, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,60))+
  geom_boxplot()

ggplot(pnn_0_0, aes(song_when, total, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,60))+
  geom_boxplot()

ggplot(pnn_0_1, aes(song_when, total, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,60))+
  geom_boxplot()

ggplot(pnn_0_2, aes(song_when, total, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,60))+
  geom_boxplot()

ggplot(pnn_0_3, aes(song_when, total, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,60))+
  geom_boxplot()

ggplot(pnn_1_sham1, aes(song_when, total, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,60))+
  geom_boxplot()

ggplot(pnn_1_sham2, aes(song_when, total, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,60))+
  geom_boxplot()

ggplot(pnn_1_sham3, aes(song_when, total, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,60))+
  geom_boxplot()

ggplot(pnn_1_0, aes(song_when, total, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,60))+
  geom_boxplot()

ggplot(pnn_1_1, aes(song_when, total, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,60))+
  geom_boxplot()

ggplot(pnn_1_1, aes(song_when, total, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,60))+
  geom_boxplot()

ggplot(pnn_1_3, aes(song_when, total, colour=song_when))+
  scale_x_discrete(limits=c("prelesion", "preinjection", "day 90"))+
  scale_y_continuous(limits=c(0,60))+
  geom_boxplot()

```

